Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-30 paper.tex
some more text of FS

                Writting BigData to Lustre is very costly compared to local 
                node storage. BigData filesystems like HDFS may not necessarily
                be the best solution for HPC as they will not only use up 
                storage on compute nodes, but also replicate the data across 
                the cluster taking up a significant amount of storage space.
                Moreover, while BigData frameworks typically execute on a 
                dedicated BigData cluster, they will be on a shared cluster in
                HPC.

                Alluxio, formerly known as tachyon, is an in-memory filesystem
                that stores lineage data rather than the data itself. It is
                assumed that recomputation of data will occur more rapidly than
                data transfer over the network. However,

>>>>

                Writting BigData to Lustre is very costly compared to local 
                node storage. BigData filesystems like HDFS may not necessarily
                be the best solution for HPC as they will not only use up 
                storage on compute nodes, but also replicate the data across 
                the cluster taking up a significant amount of storage space.
                Moreover, while BigData frameworks typically execute on a 
                dedicated BigData cluster, they will be on a shared cluster in
                HPC, with many processed trying to access the memory. The 
                following are two optimizations made for

                Alluxio, formerly known as Tachyon, is an in-memory filesystem
                that stores lineage data to offset the cost of writing data to 
                disk. The assumption that Alluxio makes is that it will be less
                costly to recompute the data that to store the data to disk and
                replicate across the network for fault tolerance. However,
                unlike Spark applications, Alluxio is meant to run indefinitely
                , making it unfavourable, in some cases, to recompute the data
                from its starting point. For this, Alluxio evaluates the 
                lineage data and selects
